Free surface computations in mantle convection models

### 2015-09-15 free-surface-paper.tex
Capitalize ASPECT
Wording

There have been several approaches to treating real free surfaces in geodynamic simulations.
\citet{zhong1996free} introduced a pseudo-free-surface formulation, where the free surface coordinate was
treated as an extra variable that was integrated in time. In this approximation, the free surface 
is approximated on the undeformed Eulerian grid by applying pressure boundary conditions on the reference surface.
The pressure is determined by a first-order Taylor series approximation of the hydrostatic pressure profile 
predicted by the surface topography.

@@

Recently, the nature of surface boundary conditions have been shown to be important for controlling the 
dynamics of subduction zone modeling.  In a benchmark study \citet{schmeling2008benchmark} performed extensive testing on the effect
of a free surface on the sinking of a slab. They found that the nature of the free surface had a large effect 
on the dynamics of the slab, affecting both the shape and the timing of sinking. Most of the 
participating codes in that benchmark used the sticky air approximation.
They found that the specific properties of the sticky air layer 
controlled the shape and timing of the slab, and the viscosity averaging scheme for areas of transitional
composition was extremely important, as the subducting slab entrained significant amounts of the sticky air.
\citet{crameri2012comparison} conducted comparisons between sticky air and true free surface models, 
demonstrating a range of parameters for sticky air which can mitigate some of the difficulties that it introduces.
A study by \citet{quinquis2011role} found that free surface boundary conditions have a large effect on 
trench migration in a subduction zone, and \citet{crameri2012free} found that a free surface combined 
with a weak crust is important for producing one-sided subduction zones.

>>>>

There have been several approaches to treating real free surfaces in geodynamic simulations.
\citet{zhong1996free} introduced a pseudo-free-surface formulation, where the free surface coordinate was
treated as an extra variable that was integrated in time. In this formulation, the free surface 
is approximated on the undeformed Eulerian grid by applying pressure boundary conditions on the reference surface.
The pressure is determined by a first-order Taylor series approximation of the hydrostatic pressure profile 
predicted by the surface topography.

@@

Recently, the nature of surface boundary conditions have been shown to be important for controlling the 
dynamics of subduction zone modeling.  In a benchmark study \citet{schmeling2008benchmark} performed extensive testing on the effect
of a free surface on the sinking of a slab. They found that the nature of the free surface had a large effect 
on the dynamics of the slab, affecting both the shape and the timing of sinking. Most of the 
participating codes in that benchmark used the sticky air approximation.
They found that the specific properties of the sticky air layer controlled the shape and timing of the slab.
Furthermore, the viscosity averaging scheme for areas of transitional
composition was extremely important, as the subducting slab entrained significant amounts of the sticky air.
\citet{crameri2012comparison} conducted comparisons between sticky air and true free surface models, 
demonstrating a range of parameters for sticky air which can mitigate some of the difficulties that it introduces.
A study by \citet{quinquis2011role} found that free surface boundary conditions have a large effect on 
trench migration in a subduction zone, and \citet{crameri2012free} found that a free surface combined 
with a weak crust is important for producing one-sided subduction zones.
